H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-13 slides-agu/presentation.tex
Close to final draft, we hope

\begin{frame}{Motivating Example}
  What to do after Sandy? \citep{CityofNewYork:2013uh}
  \begin{figure}
    \centering
    \includegraphics[height=0.3\textheight]{three-barriers.png}
    \includegraphics[height=0.3\textheight]{flood-concept.png}
    \caption{
      A large, permanent structure (L) would lock in $\approx \$25 \text{billion}$; a portfolio of smaller investments (R) may be more flexible and robust.
    }
  \end{figure}
  \pause
  \begin{alertblock}{Scheduling and sequencing:}
    When (and how) to build a flexible portfolio vs mega-project
  \end{alertblock}
\end{frame}

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents[hideallsubsections]
\end{frame}

@@

\begin{frame}{Idea 2: Hydroclimate Systems Vary on Many Scales}
  Inter-annual to multi-decadal variability very important in near future (\ie, for small $M$) \citep{Hodgkins:2017hw}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.55\textheight,keepaspectratio=true]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How to identify \& predict}
    cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
 \end{alertblock}
 \pause
  \begin{figure}
    \includegraphics[width=\textwidth]{flowchart.pdf}
  \end{figure}
  defining $P^* \def \mathbb{P} \qty(X > X^*)$, the insurance premium
  \begin{equation*}
    R = \mathbb{E}\qty[ P^*] + \lambda \mathbb{V} \qty[P^*]
  \end{equation*}
\end{frame}

\begin{frame}{Stationary Scenario (LFV Only)}
  With limited data, the uncertainties caused by extrapolating from complex models lead to poor performance.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario I (Secular Change Only)}
  For long $M$, it's important to estimate the trend -- but this works well only if $N$ also long.
  For short $M$ and short $N$, the uncertainty added by estimating a trend is not worth the bias reduction.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{secular-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario II (Secular Change + LFV)}
  As the system becomes more complex, more data is needed to understand it.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-secular-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

>>>>

\begin{frame}{Motivating Example}
  What to do after Sandy? \citep{CityofNewYork:2013uh}
  \begin{figure}
    \centering
    \includegraphics[height=0.35\textheight]{three-barriers.png}~
    \includegraphics[height=0.35\textheight]{dull-disasters.png}\\
    \includegraphics[height=0.3\textheight]{flood-concept.png}~
    \includegraphics[height=0.3\textheight]{coastal-resiliency.png}
  \end{figure}
\end{frame}

@@

\begin{frame}{Idea 2: Hydroclimate Systems Vary on Many Scales}
  Inter-annual to multi-decadal cyclical variability key (for small $M$)
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.55\textheight,keepaspectratio=true]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

@@

\begin{frame}{Experiment Setup}
  \begin{alertblock}{Research Objective}
    How well can one identify \& predict cyclical and secular climate signals over a finite planning period ($M$),  given limited information?
 \end{alertblock}
  Let $P^* \def \mathbb{P} \qty(X > X^*)$.
  Note that the insurance premium (or risk factor) is:
  \begin{equation*}
    R = \mathbb{E}\qty[ P^*] + \lambda \mathbb{V} \qty[P^*]
  \end{equation*}
  \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-Stationary-Trend.pdf}
      \end{figure}
    \end{column}
    \begin{column}{0.5\textwidth}
      Systematic, stylized experiments:
      what happens as we vary $M$, $N$, climate structure, estimating model?
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Stationary Scenario (LFV Only)}
  \emph{With limited data, the uncertainties caused by extrapolating from complex models lead to poor performance.}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario I (Secular Change Only)}
  \emph{Long planning periods need trend estimation, but this demands lots of information.
  For short planning periods, simple models may be better.}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{secular-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario II (Secular Change + LFV)}
  \emph{As the system becomes more complex, more data is needed to understand it.}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-secular-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}
